Image reconstruction of stellar objects with Intensity Interferometry using Generative Adversarial Networks

### 2025-02-02 Phase_II/draft/II.tex
changes in bib file

\textcolor{blue}{Subsequently, during the opening decades of the current century, proposals to use the Imaging Atmospheric Cherenkov Telescope (IACT) facilities for carrying out Stellar Intensity Interferometry (SII) observations were put forth \citep{LeBohec2006, Nunez2010stellar, Nunez2012High, Dravins2013}. Such observations, it was suggested, could be carried out during bright moon-lit nights during which $\gamma$-ray observations using upper atmospheric Cherenkov showers were not feasible. This idea had the potential of enhancing the scientific output of the existing facilities like VERITAS, MAGIC and HESS. Subsequent SII obserations at these facilities providing the proof of concept have been published \citep{abeysekara2020demonstration, Abe2024MAGIC, Zmija2023}. }

>>>>

\textcolor{blue}{Subsequently, during the opening decades of the current century, proposals to use the Imaging Atmospheric Cherenkov Telescope (IACT) facilities for carrying out Stellar Intensity Interferometry (SII) observations were put forth \citep{LeBohec2006, nunez2010stellar, nunez2012high, Dravins2013}. Such observations, it was suggested, could be carried out during bright moon-lit nights during which $\gamma$-ray observations using upper atmospheric Cherenkov showers were not feasible. This idea had the potential of enhancing the scientific output of the existing facilities like VERITAS, MAGIC and HESS. Subsequent SII obserations at these facilities providing the proof of concept have been published \citep{abeysekara2020demonstration, Abe2024MAGIC, Zmija2023}. }
